---
title: "HW Quant Wk.5"
author: "Teepawat A."
date: "7 September 2018"
output:
  pdf_document: default
  html_document: default
---

```{r}
library(quantmod)
library(timeSeries)
```

## Load stock data named "Alibaba Group"(BABA)
Plot close price of BABA for investigation
```{r}
getSymbols('BABA')
return = na.omit(diff(BABA))
plot(BABA$BABA.Close)
```

## Create return of Alibaba group's stock price
```{r}
return = na.omit(diff(BABA$BABA.Close))
plot(return)
```
## Next, we will prove 3 facts of return
## 1. distribution of returns is not normal

```{r}
hist(return, breaks = "Scott", probability = T)
curve(dnorm(x,mean=mean(return),sd=sd(return)),col='red',add=T,main="")
```
For Alibaba Group's stock, the distribution seem like "Normal" but a little skew to the left.

## 2.There is almost no correlations between returns for different days.   
```{r}
acf(return)
```
From the graph above, the second rule is quite true since autocorrelations are quite small.

# 3. There is positive dependence(autocorrelations) between absolute returns on nearby days, and likewise for squared returns.

```{r}
par(mfrow = c(2,1))
acf(abs(return))
acf(return^2)
```
It is confirmed that there is positive dependency  between absolute return in nearby days.
